### 2016-06-29 publications/Journal/models.tex
Added another reference

In this section, we evaluate the performance of different synchronization protocols in dxex.
We also compare to adevs, currently one of the most efficient simulation kernels~\cite{DEVSSurvey}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both sequential and parallel simulation.

>>>>

In this section, we evaluate the performance of different synchronization protocols in dxex.
We also compare to adevs~\cite{adevs}, currently one of the most efficient simulation kernels~\cite{DEVSSurvey,DEVStoneJournal}, to show that our modularity does not impede performance.
CPU time and memory usage is compared for both sequential and parallel simulation.
